Galaxy Zoo: Morphological Classifications for 120,000 Galaxies in HST Legacy Imaging

### 2016-05-29 writeup/gz_hubble_data.tex
Fixed caption on Table 3. Closes #164.
References to Kaviraj+14a,b

Theoretical predictions for the morphology of galaxies as a function of
redshift are primarily computed within the $\Lambda$CDM cosmological framework.
Full treatments model gravitational interactions between baryons and dark
matter, hydrodynamics of the gas, and baryonic physics related to star
formation and evolution. The most advanced simulations now span volumes up to
$\sim100$~Mpc$^3$ while simultaneously resolving the smaller ($<1$ kpc) scales
necessary to reproduce the influence of baryonic physics \citep{vog14a,sch15}.
Such simulations predict clustering of galaxies on large scales in a
hierarchical assembly model \citep{sil12}. The structure of individual galaxies
is affected by their merger history \citep{too72,ste02,hop10}, local
environment \citep[\eg, the morphology-density relation;][]{dre80}, initial
dark halo mass, secular evolution rate, and many other factors. Morphologies of
individual simulated high-mass galaxies at $z\sim2-3$ commonly show kpc-scale
``clumpy'' structures, with few galaxies that are either smooth or well-ordered
spirals; asymmetric galaxies with strong density contrasts dominate simulated
populations in the early Universe until at least $z\sim1$ \citep{bel12,gen14}.

@@

\begin{table*}
\caption{Correctable fractions for the top-level task in GZH, split by survey.}\label{tbl:hubble_debiasable}
\begin{tabular}{lcrrrrr|r}
\hline\hline
                                   & Correction type & AEGIS   & COSMOS & GEMS  & GOODS-N & GOODS-S  &  Total  \\
                                   &                 &         &        &       & 5-epoch & 5-epoch  &         \\
\hline
correctable                        & 0               & 2,908   & 21,169 & 2,802 & 1,459   & 1,189    &  29,527 \\
lower-limit                        & 1               &   833   &  5,169 & 1,021 & 1,377   & 1,267    &   9,667 \\
no correction needed ($z \le 0.3$) & 2               &   955   & 10,870 & 1,175 &   415   &   400    &  13,815 \\ 
not enough information (NEI)       & 3               & 2,677   & 43,058 & 3,559 & 2,077   & 2,184    &  53,555 \\
no redshift information            & 4               & 1,134   &  4,688 &   530 &   687   &   102    &   7,141 \\
\hline
total                              &                 & 8,507   & 84,954 & 9,087 & 6,015   & 5,142    & 113,705 \\
\hline\hline
\end{tabular}
\end{table*}

>>>>

Theoretical predictions for the morphology of galaxies as a function of
redshift are primarily computed within the $\Lambda$CDM cosmological framework.
Full treatments model gravitational interactions between baryons and dark
matter, hydrodynamics of the gas, and baryonic physics related to star
formation and evolution. The most advanced simulations now span volumes up to
$\sim100$~Mpc$^3$ while simultaneously resolving the smaller ($<1$ kpc) scales
necessary to reproduce the influence of baryonic physics \citep{vog14a,sch15}.
Such simulations predict clustering of galaxies on large scales in a
hierarchical assembly model \citep{sil12}. The structure of individual galaxies
is affected by their merger history \citep{too72,ste02,hop10,kav14,kav14a}, local
environment \citep[\eg, the morphology-density relation;][]{dre80}, initial
dark halo mass, secular evolution rate, and many other factors. Morphologies of
individual simulated high-mass galaxies at $z\sim2-3$ commonly show kpc-scale
``clumpy'' structures, with few galaxies that are either smooth or well-ordered
spirals; asymmetric galaxies with strong density contrasts dominate simulated
populations in the early Universe until at least $z\sim1$ \citep{bel12,gen14}.

@@

\begin{table*}
\caption{Number of correctable galaxies for the top-level task in GZH, split by \hst{} survey.}\label{tbl:hubble_debiasable}
\begin{tabular}{lcrrrrr|r}
\hline\hline
                                   & Correction type & AEGIS   & COSMOS & GEMS  & GOODS-N & GOODS-S  &  Total  \\
                                   &                 &         &        &       & 5-epoch & 5-epoch  &         \\
\hline
correctable                        & 0               & 2,908   & 21,169 & 2,802 & 1,459   & 1,189    &  29,527 \\
lower-limit                        & 1               &   833   &  5,169 & 1,021 & 1,377   & 1,267    &   9,667 \\
no correction needed ($z \le 0.3$) & 2               &   955   & 10,870 & 1,175 &   415   &   400    &  13,815 \\ 
not enough information (NEI)       & 3               & 2,677   & 43,058 & 3,559 & 2,077   & 2,184    &  53,555 \\
no redshift information            & 4               & 1,134   &  4,688 &   530 &   687   &   102    &   7,141 \\
\hline
total                              &                 & 8,507   & 84,954 & 9,087 & 6,015   & 5,142    & 113,705 \\
\hline\hline
\end{tabular}
\end{table*}
